---
title: "Day 1 - Intro"
format:
  html:
    theme: litera
    toc: true
    number-sections: true
---

## Welcome!

[**Purpose of this workshop**]{.ul}

R as a calculator

```{r}

```

Boolean operators (logical result)

\`\>\`, \`\<\`, \`==\`, \`!=\`

```{r}

```

Objects

```{r}

```

### Packages

An R package is a collection of functions, data, and documentation that extends the capabilities of base R [\[R4DS\]](https://r4ds.had.co.nz/introduction.html#r).

### Functions

```{r}
# read data
```

### tidyverse

The packages in the tidyverse share a common philosophy of data and R programming, and are designed to work together naturally.

-   \`**select()**\`: selects **COLUMNS**. - from \`dplyr\`

    -   Helper functions:

        -   \`starts_with("abc")\`

        -   \`ends_with("xyz")\`

        -   \`contains("ijk")\`

        -   \`matches("(.)\\\\1")\`: variables that match a regular expression (repeated characters)

        -   \`num_range("x", 1:3)\`

        -   dplyr::select()

-   \`**filter()**\`: selects **ROWS** that satisfty a logic test

    -   Helper function: \`between()\`

-   \`arrange()\`: reorders rows

-   \`**mutate()**\`: creates a new column. \`.keep\` = T/F

-   \`rename()\`: renames columns

## Good coding habits

-   Put all \`library()\` calls at the top of the script.

-   Organize your files into \`data\`, \`notebook\`/\`markdown\`, \`output\`.

-   Comment your code.

-   Object names:

    -   Don't start with numbers

    -   Shortest understandable

-   Each %>% followed by a new line.

-   Avoid long lines (start a new line after comma).
