---
title: "Week 2"
format:
  html:
    theme: litera
    toc: true
    number-sections: true
---


## 1. Libraries  
```{r}

```

## Review on tidyverse functions  
```{r}
# mutate

# filter

# dplyr::select
```

## New functions  

### Data wrangling  
```{r}
# pivot longer

# pivot wider
```

### Names   
```{r}
# case_when


```

### left_join  
```{r}

```

# ggplot2  

- [Some cool examples](https://www.cedricscherer.com/top/dataviz/).  

```{r}
ndata_plant <- readxl::read_xlsx("../data/N_initiative/8.Yield_Plant_Measurements.xlsx", sheet = 2)
glimpse(ndata_plant)
```

```{r}
ndata_plant %>% 
  mutate(across(where(is.character), ~na_if(., ".")))
```


## Structure  


1. Data  
2. Layers `geom_*()` and `stat_*()`  
3. Aesthetics `aes()`  
4. Scales `scale_*()`  
5. Coordinate system `coord_*()`  
6. Facets `facet_*()` arrangement of the data into a grid of plots  
7. Visual themes `theme()` visual defaults  

### Start with a white canvas  

```{r}

```

### Add geoms  


### Arrange aesthetics  


### Scales  


### Coordinates  


### Facets  


### Themes  
