---
title: "Week 2"
format:
  html:
    theme: litera
    toc: true
    number-sections: true
---


## 1. Libraries  
```{r}
library(tidyverse)
```

```{r}
df <- read.csv("../data/weather_tidy.csv")
```

## Review on tidyverse functions  
```{r}
# mutate
df %>% 
  mutate(AIrTemp_mean = (AirTemp_max+AirTemp_min)/2)

# filter
df %>% 
  filter(AirTemp_max>10)
# dplyr::select

df_new <- df %>%
  dplyr::select(location, year)
```

## New functions  

### Data wrangling  
```{r}
# pivot longer
df_temp <- read.csv("../data/weather_tidy.csv") %>% 
  dplyr::select(location:AirTemp_min) %>% 
  pivot_longer(cols = c(AirTemp_max, AirTemp_min))
```

```{r}
df <- read.csv("../data/weather_tidy.csv")
# group_by
df %>% 
  separate(date, c("day", "month"), sep = "-") %>% 
  group_by(month) %>%
  summarise(month_mean_max = mean(AirTemp_max),
            month_mean_min = mean(AirTemp_min))
```

### Names   
```{r}
# case_when


```

### left_join  
```{r}
left_join()
```

# ggplot2  

- [Some cool examples](https://www.cedricscherer.com/top/dataviz/).  
- Rgraphgallery  

```{r}
# 49 trials of N fertilization in corn across several states in the US
ndata_plant <- readxl::read_xlsx("../data/N_initiative/8.Yield_Plant_Measurements.xlsx", sheet = 'All_Plant')

glimpse(ndata_plant)
colnames(ndata_plant)
summary(ndata_plant)
```

```{r}
df %>% 
  mutate(across(AirTemp_max:AirTemp_min, 
                ~round(., 0)))
  # mutate(AirTemp_max = round(AirTemp_max, 0),
  #        AirTemp_min = round(AirTemp_min, 0))
```


```{r}
ndata_plant <- ndata_plant %>% 
  mutate(across(where(is.character), 
                ~na_if(., "."))) %>% 
  mutate(across(VTPwet:Yield_SY,
                ~as.numeric(.)))
```


## Structure  

```{r}
ggplot(ndata_plant)
```

### 1. Data. Start with a white canvas  

white canvas:

```{r}
ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))
```


### 2. Add geoms  
Layers of `geom_*()` and `stat_*()`  
```{r}
ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))+
  geom_point()
```

### 3. Arrange aesthetics (aes())  

```{r}
ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))+
  geom_point(aes(color = State,
                 shape = factor(Year)),
             size =.3)
```

### 4. Scales  `scale_*()`   
```{r}
ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))+
  geom_point(aes(color = State,
                 shape = factor(Year)),
             size =.3)+
  scale_color_viridis_d()
```

### 5. Coordinate system `coord_*()`  
```{r}

ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))+
  geom_point(aes(color = State,
                 shape = factor(Year)),
             size =.3)+
  scale_color_viridis_d()+
  coord_cartesian(xlim = c(25000,30000))
```

### 6. Facets `facet_*()` arrangement of the data into a grid of plots  
```{r}
ndata_plant %>% 
  ggplot(aes(x = Plnt_Pop, y = Yield_SY))+
  geom_point(aes(color = factor(Year),
                 shape = factor(Year)),
             size =.3)+
  scale_color_viridis_d()+
  facet_wrap(~State)
```



7. Visual themes `theme()` visual defaults  

```{r}
# try +theme_bw() or +theme_classic()
```


